Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-29 docs/thesis/slides/apresentacao_unb.tex
reduced full version

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Discriminative Sensing Based on Signal Processing for Information Security Analysis}
\subtitle{\small{Ph.D. Thesis Qualification}}
\date{\today}
\author{\texttt{Thiago P. de B. Vieira \newline \textbf{Advisor:} João Paulo C. L. da Costa} }
\institute{Universidade de Brasília 
	\par \scriptsize{Departamento de Engenharia Elétrica - ENE/FT}
	\par \scriptsize{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}
}

\hypersetup{
	pdfauthor = {Thiago P. de B. Vieira},
	pdfsubject = {Discriminative Sensing Based on Signal Processing for Information Security Analysis},
	pdfkeywords = {Signal Processing, Information Security Analysis},
	pdfmoddate= {/home/thiago/dev/projects/discriminative-sensing/docs/thesis/slides},
	pdfcreator = {Sublime and Latex}
}

@@

%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%
%	TABLE OF CONTENTS: OVERVIEW
%
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\section{Introduction}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Motivation
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Motivation}
	It is necessary investments to detect \textbf{novel attacks and their variations}
	\begin{itemize}
		\item Signal processing schemes have being applied to detect malicious traffic;		
	\end{itemize}
	Secure mobile cloud architecture is challenging, specially in \textbf{offline mode}
	\begin{itemize}
		\item Signal processing can be applied to \textbf{behavioral analysis of mobile apps in offline mode};		
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Motivation
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Motivation}
	\textbf{Fraud detection} of \textbf{Mobile Money Transactions} has been motivating investments
	\begin{itemize}
		\item The \textbf{extraction of relevant information} from \textbf{raw or big} data is useful for classification problems and for security analysis.;
		\item Imbalanced data is challenging for classification related to anomaly detection, novelty detection, fraud detection and attack detection;
		\item \textbf{Tensor-based} algorithms for \textbf{dictionary learning} can improve \textbf{discriminative sensing} for classification in information security analysis;
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Problem Statement
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Problem Statement}
	\textbf{This thesis} outlines the development and evaluation of approaches based on \textbf{signal processing for information security analysis}...
	\begin{itemize}
		\item To make the data \textbf{discriminative} for network attack detection, mobile malicious behavior analysis and fraud detection in mobile money transactions.
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Problem Statement
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Problem Statement}
	We propose an approach based on \textbf{signal processing techniques for detection of malicious traffic in computer networks}
	\begin{itemize}
		\item Signal processing formulation as legitimate traffic, malicious traffic and noise;
		\item MOS and eigenvalue analysis are applied to network attack detection;
		\item Eigen similarity analysis identify accurate time and network ports under attack;
		\item Evaluation through experimental scenario and the DARPA 1998 dataset.
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Problem Statement
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Problem Statement}
	This thesis also proposes an \textbf{approach malicious behavior detection in mobile apps}
	\begin{itemize}
		\item An architecture for mobile security analysis;
		\item Offline user behavior analysis based on MOS;
		\item Scenario analysis for feature selection;
		\item Processing time evaluation in mobile devices.
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Problem Statement
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Problem Statement}
	We also propose a \textbf{tensor-based dictionary learning method for fraud detection from imbalanced data} 
	\begin{itemize}
		\item To evidentiate the \textbf{discriminative sensing of a fraud detection dataset};
		\item Sparse representation based classification (SRC) through learning a tensor-based dictionary;
		\item Apply the learned dictionaries to reconstruct a test signal and classify it as fraud or legitimate;
		\item Classify fraud classification of mobile money transactions according to the reconstruction error.
	\end{itemize}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Contributions
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Contributions}
% 	\begin{enumerate}
% 		\item An approach based on \textbf{eigen similarity analysis} for extracting detailed information about accurate time and network ports under network attack;
% 		\item Computational \textbf{complexity analysis} of the proposed framework;
% 		\item An architecture and techniques for \textbf{offline behavioral analysis} of a corporate mobile client security architecture;
% 		\item A \textbf{tensor-based dictionary learning} approach for \textbf{fraud detection} in mobile payment transactions;
% 	\end{enumerate}
% \end{frame}

%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%
%	SECTION: Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks
%
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\section{Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Introduction
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Introduction}
	\begin{itemize}
		\item We model the network traffic as a signal processing formulation (\textbf{legitimate traffic, malicious traffic and noise});
		\item The proposed technique is based on eigenvalue analysis, model order selection (MOS) and similarity analysis;
		\item MOS and eigenvalue analysis are applied to detect time frames under attack;
		\item Eigen similarity analysis for extracting detailed time and network ports under attack;
		\item We conduct a performance evaluation for complexity analysis and processing time.
	\end{itemize}
\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Related works
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Related works}

	\begin{itemize}
		\item Classical methods typically employ data mining [39, 34, 70] and regular file analysis [76] to detect patterns that indicate the presence of specific attacks in network traffic;
		\item Callegari \emph{et al} [104] propose a PCA-based method for identifying the traffic flows responsible for an anomaly detected at the aggregate level and evaluated their proposal through a dataset with synthetic anomalies added in the data. However, Callegari \emph{et al} \textbf{focus on flood attack detection}, not addressing probe attack detection, and their approach relies on \textbf{visual analysis}.
	\end{itemize}

@@

	\begin{itemize}
		\item Lee \emph{et al.} [61] propose OverSampling PCA, determines the \textbf{anomaly} according to the variation of \textbf{eigenvector by similarity analysis and over sampling}. We apply \textbf{MOS for attack detection} and \textbf{similarity analysis for identification} of time and ports under attack;
		\item Lu and Ghorbani [63] proposed a \textbf{network anomaly} detection model based on \textbf{network flow, wavelet approximation, and system identification theory}. However, their work requires a \textbf{training} and presents \textbf{limitations} on identification of behaviors without \textbf{significant outliers}.
	\end{itemize}

@@

	We focus on \textbf{probe} and \textbf{flooding} attacks;

	Two scenarios: 
	\begin{itemize}
		\item A \textbf{synthetic dataset} as a signal superposition of legitimate traffic, noise and malicious traffic;
		\item Selected cases of \textbf{DARPA dataset} that reproduce probe and flooding attacks.
	\end{itemize}

@@

	Network traffic:

	\begin{equation}\label{eq:eq01}
		\boldsymbol{X}^{(q)} = \boldsymbol{U}^{(q)} + \boldsymbol{N}^{(q)} + \boldsymbol{A}^{(q)},
	\end{equation}

@@

	Each row is a TCP or UDP port, and each column represents time bins (minute)

@@

	\begin{figure}[h!]
	     \centering 
	     \includegraphics[width=9cm]{../figures/fig04.png}
	     \caption{Network traffic of user independent operations for network management.}
	     \label{fig:2_fig4}
	\end{figure}

@@

	\begin{figure}[h!]
	     \centering 
	     \includegraphics[width=9cm]{../figures/fig06.png}
	     \caption{Large amount of “UDP echo” requests and replies, causing packet flooding.}
	     \label{fig:2_fig6}
	\end{figure}

	\begin{figure}[h!]
	     \centering 
	     \includegraphics[width=9cm]{../figures/fig07.png}
	     \caption{Connection attempts in order to identify active ports.}
	     \label{fig:2_fig7}
	\end{figure}

\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: DARPA Dataset
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}{DARPA Dataset}

	\begin{itemize}
		\item 7 weeks of sniffed traffic saved into raw TCPDUMP packet data, from inside and outside origins, with labeled attacks;
		\item The most cases of DoS focus on exploit system vulnerabilities instead of on flooding attack;
		\item We select the cases that reproduce probe and flooding attacks.
	\end{itemize}

@@

	For \textbf{flooding} detection, calculate the \textbf{sample covariance matrix} $\boldsymbol{\hat{R}}_{yy}^{(q)}$ of the zero mean samples given by
	\begin{equation}\label{eq:eq02}
		\boldsymbol{y}_{m}^{(q)} = \boldsymbol{x}_{m}^{(q)} - \bar{\boldsymbol{x}}_{m}^{(q)}.
	\end{equation}

	the sample covariance matrix $\boldsymbol{\hat{R}}_{yy}^{(q)}$ can be calculated as follows
	\begin{equation}\label{eq:eq03}
		\boldsymbol{\hat{R}}_{yy}^{(q)} = \frac{1}{N}\boldsymbol{Y}^{(q)}\boldsymbol{Y}^{(q)^{\rm T}}.
	\end{equation}

	For \textbf{probing} detection, compute the \textbf{sample covariance} $\boldsymbol{\hat{R}}_{zz}^{(q)}$ whose variables have \textbf{zero mean and unitary standard deviation} as follows
	\begin{equation}\label{eq:eq04}
		\boldsymbol{z}_{m}^{(q)} = \frac{\boldsymbol{x}_{m}^{(q)} - \bar{\boldsymbol{x}}_{m}^{(q)}}{\boldsymbol{\sigma}_{m}^{(q)}}.
	\end{equation}

	The sample covariance matrix $\boldsymbol{\hat{R}}_{zz}^{(q)}$ can be calculated via 
	\begin{equation}\label{eq:eq05}
		\boldsymbol{\hat{R}}_{zz}^{(q)} = \frac{1}{N}\boldsymbol{Z}^{(q)}\boldsymbol{Z}^{(q)^{\rm T}}.
	\end{equation}

	we refer to $\boldsymbol{\hat{R}}_{yy}$ and $\boldsymbol{\hat{R}}_{zz}$ as a matrix $\boldsymbol{C}$

	Compute eigenvalue decomposition (EVD) to obtain the vector of eigenvalues $\boldsymbol{e}^{(q)}$ associated with each matrix (time frame $q$), according to (\ref{eq:eq060}).
	\begin{equation}\label{eq:eq06}
	\boldsymbol{C}^{(q)} = \boldsymbol{V}^{(q)}\boldsymbol{\Lambda}^{(q)}\boldsymbol{V}^{(q)^{\rm T}},
	\end{equation}
	\begin{equation}\label{eq:eq060}
	\boldsymbol{e}^{(q)} = \rm diag(\boldsymbol{\Lambda}^{(q)}),
	\end{equation}

	The eigenvalues should be sorted in descending order, i.e., $\lambda_{1}^{(q)} > \lambda_{2}^{(q)} > \lambda_{3}^{(q)} > ... > \lambda_{m}^{(q)}$.

	\begin{equation}\label{eq:eq07}
		\boldsymbol{E} =
		\begin{bmatrix}
			\color{red}\lambda_1^{(1)} & \color{red}\lambda_1^{(2)} & \color{red}\lambda_1^{(3)} & \cdots & \color{red}\lambda_1^{(Q)} \\
			\lambda_2^{(1)} & \lambda_2^{(2)} & \lambda_2^{(3)} & \cdots & \lambda_2^{(Q)} \\
			\lambda_3^{(1)} & \lambda_3^{(2)} & \lambda_3^{(3)} & \cdots & \lambda_3^{(Q)} \\
			\vdots & \vdots & \ddots & \vdots  \\
			\lambda_m^{(1)} & \lambda_m^{(2)} & \lambda_m^{(3)} & \cdots & \lambda_m^{(Q)} \\
		\end{bmatrix}.
	\end{equation}

	\begin{equation}\label{eq:eq08}
		\boldsymbol{e}_{\rm max} = \boldsymbol{E}\{:,1\} = [ \lambda_1^{(1)}, \lambda_1^{(2)} ... \lambda_1^{(Q)}]
	\end{equation}

\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: MOS Scheme
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}{MOS Scheme}

	\begin{itemize}
		\item Traditionally the MOS schemes are applied for the eigenvalues of the vector $\boldsymbol{e}^{(q)}$;
		\item $\boldsymbol{e}_{\rm max}$ is sorted in descending order, producing $\sim\boldsymbol{e}_{\rm max}$, that is used as input parameter for MOS schemes, according to $\hat{d} = \rm{MOS}(\sim\boldsymbol{e}_{\rm max})$.
		\item $\hat{d}$ is the estimated number of time frames under attack.
	\end{itemize}

\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Eigenvalue Analysis
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}{Eigenvalue Analysis}

	Through eigenvalue analysis, we identify the time frames $q$ under attack

@@

	The reference eigenvectors $\boldsymbol{v}^{(q)}$ is calculated from the traffic without attack.

@@

	The resultant $\boldsymbol{X}_{(n)}$ is necessary to obtain $\boldsymbol{v}_{(n)}$, through (\ref{eq:eq06}).

@@

	Our approach presents average results if compared to two well known and highly adopted classifier algorithms for fraud detection from mobile money transactions.

>>>>

\usepackage[backend=bibtex, style=numeric, defernumbers=true]{biblatex}
\addbibresource{../references.bib}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

@@

\title{Discriminative Sensing Based on Signal Processing for Information Security Analysis}
\subtitle{\small{Ph.D. Thesis Qualification}}
\author{\texttt{Thiago P. de B. Vieira \newline \textbf{Advisor:} João Paulo C. L. da Costa} }
\institute{
		\scriptsize{Universidade de Brasília}
	\\ 	\scriptsize{Departamento de Engenharia Elétrica - ENE/FT}
	\\ \scriptsize{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}}

@@

%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%
%	TABLE OF CONTENTS: OVERVIEW
%
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\section{Introduction}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Motivation
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Motivation}
	\begin{itemize}
		\item It is necessary investments to detect \textbf{novel attacks and their variations};
		\item Secure mobile cloud architecture is challenging, specially in \textbf{offline mode}
		\item \textbf{Fraud detection} of \textbf{Mobile Money Transactions} has been motivating investments
		\begin{itemize}
			\item The \textbf{extraction of relevant information} from \textbf{raw or big data} is useful for classification problems and for security analysis.;
			\item \textbf{Imbalanced data is challenging} for classification related to anomaly detection, novelty detection, fraud detection and attack detection.
		\end{itemize}
	\end{itemize}
\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Problem Statement
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Problem Statement}
	\textbf{This thesis} outlines the \textbf{development} and evaluation of approaches based on \textbf{signal processing for information security analysis}...
	\begin{itemize}
		\item To make the data \textbf{discriminative for network attack detection, mobile malicious behavior analysis and fraud detection.}
	\end{itemize}
\end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Problem Statement
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Problem Statement}
% 	We propose an approach for \textbf{identification of malicious traffic in computer networks}
% 	\begin{itemize}
% 		\item We use\textbf{largest eigenvalues and MOS} to \textbf{network attack detection};
% 		\item We propose \textbf{Eigen similarity analysis} identify \textbf{accurate time and ports} under attack;
% 	\end{itemize}
% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Problem Statement
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Problem Statement}
% 	This thesis also proposes an \textbf{approach for malicious behavior detection in mobile apps}
% 	\begin{itemize}
% 		\item An \textbf{architecture} for mobile security analysis;
% 		\item \textbf{Offline user behavior analysis} based on MOS;
% 		\item Scenario analysis for \textbf{feature selection};
% 		\item \textbf{Processing time} evaluation in \textbf{mobile} devices.
% 	\end{itemize}
% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Problem Statement
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Problem Statement}
% 	We finally propose a \textbf{tensor-based dictionary learning method for fraud detection} 
% 	\begin{itemize}
% 		\item Sparse representation based \textbf{classification} (SRC) through learning a \textbf{tensor-based} dictionary;
% 		\item Apply the \textbf{learned dictionaries to reconstruct} a test signal;
% 		\item \textbf{Fraud classification} of mobile money transactions according to the \textbf{reconstruction error}.
% 	\end{itemize}
% \end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Contributions
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Contributions}
% 	\begin{enumerate}
% 		\item An approach based on \textbf{eigen similarity analysis} for extracting detailed information about accurate time and network ports under network attack;
% 		\item Computational \textbf{complexity analysis} of the proposed framework;
% 		\item An architecture and techniques for \textbf{offline behavioral analysis} of a corporate mobile client security architecture;
% 		\item A \textbf{tensor-based dictionary learning} approach for \textbf{fraud detection} in mobile payment transactions;
% 	\end{enumerate}
% \end{frame}

%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%
%	SECTION: Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks
%
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\section{Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Introduction
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Introduction}
	\begin{itemize}
		\item The network traffic is modeled as a signal processing formulation (\textbf{legitimate traffic, malicious traffic and noise});
		% \item The proposed technique is based on eigenvalue analysis, model order selection (MOS) and similarity analysis;
		\item MOS and eigenvalue analysis are applied to detect time frames under attack;
		\item We \textbf{propose Eigen similarity analysis} for extracting detailed time and network ports under attack;
		\item We \textbf{conduct a performance evaluation} for complexity analysis and processing time.
	\end{itemize}
\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Related works
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Related works}

	\begin{itemize}
		% \item \textbf{Classical methods typically employ data mining} \cite{he2008applying,ghourabi2010data,osanaiye2016distributed} and regular file analysis \cite{raynal2004honeypot} to detect patterns that indicate the presence of specific attacks in network traffic;
		\item Callegari \emph{et al} \cite{Zonglin2009} propose a \textbf{PCA-based} method for identifying the traffic flows responsible for an anomaly detected at the aggregate level and evaluated their proposal through a dataset with synthetic anomalies added in the data. However, Callegari \emph{et al} \textbf{focus on flood attack detection, not addressing probe} attack detection, and their approach relies on \textbf{visual analysis}.
	\end{itemize}

@@

	\begin{itemize}
		\item Lee \emph{et al.} \cite{Lee2013} propose OverSampling PCA, determines the \textbf{anomaly} according to the variation of \textbf{eigenvector by similarity analysis and over sampling}. We apply \textbf{MOS for attack detection} and \textbf{similarity analysis for identification} of time and ports under attack;
		\item Lu and Ghorbani \cite{Lu2009} proposed a \textbf{network anomaly} detection model based on \textbf{network flow, wavelet approximation, and system identification theory}. However, their work requires a \textbf{training} and presents \textbf{limitations} on identification of behaviors without \textbf{significant outliers}.
	\end{itemize}

@@

	We focus on \textbf{probe} and \textbf{flooding} attacks for two scenarios: 
	\begin{itemize}
		\item A \textbf{synthetic dataset} as a signal superposition of legitimate traffic, noise and malicious traffic;
		\item Selected cases of \textbf{DARPA dataset} that reproduce probe and flooding attacks.
	\end{itemize}

@@

	Network traffic as a signal superposition matrix:
	\begin{equation}\label{eq:eq01}
		\boldsymbol{X}^{(q)} = \boldsymbol{U}^{(q)} + \boldsymbol{N}^{(q)} + \boldsymbol{A}^{(q)},
	\end{equation}

	The data is divided into $Q$ time frames.

@@

	Each \textbf{row} is a \textbf{TCP or UDP port}, and each \textbf{column} represents \textbf{time} bins (minute).

@@

\end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Synthetic Dataset
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Synthetic Dataset}

% 	\begin{figure}[h!]
% 	     \centering 
% 	     \includegraphics[width=9cm]{../figures/fig04.png}
% 	     \caption{Network traffic of user independent operations for network management.}
% 	     \label{fig:2_fig4}
% 	\end{figure}

% \end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Synthetic Dataset
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}[c]{Synthetic Dataset}

@@

\end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Synthetic Dataset
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Synthetic Dataset}

% 	\begin{figure}[h!]
% 	     \centering 
% 	     \includegraphics[width=9cm]{../figures/fig06.png}
% 	     \caption{Large amount of “UDP echo” requests and replies, causing packet flooding.}
% 	     \label{fig:2_fig6}
% 	\end{figure}

% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Synthetic Dataset
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}[c]{Synthetic Dataset}

% 	\begin{figure}[h!]
% 	     \centering 
% 	     \includegraphics[width=9cm]{../figures/fig07.png}
% 	     \caption{Connection attempts in order to identify active ports.}
% 	     \label{fig:2_fig7}
% 	\end{figure}

% \end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: DARPA Dataset
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}{DARPA Dataset}

	\begin{itemize}
		\item \textbf{7 weeks} of sniffed traffic saved into raw TCPDUMP packet data, from \textbf{inside and outside} origins, with \textbf{labeled} attacks;
		\item The most cases of \textbf{DoS focus on exploit} system vulnerabilities instead of on \textbf{flooding} attack;
		\item We select the cases that reproduce \textbf{probe and flooding} attacks.
	\end{itemize}

@@

\end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Proposed Framework
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Proposed Framework}

% 	For \textbf{flooding} detection, calculate the \textbf{sample covariance matrix} $\boldsymbol{\hat{R}}_{yy}^{(q)}$ of the zero mean samples given by
% 	\begin{equation}\label{eq:eq02}
% 		\boldsymbol{y}_{m}^{(q)} = \boldsymbol{x}_{m}^{(q)} - \bar{\boldsymbol{x}}_{m}^{(q)}.
% 	\end{equation}

% 	the sample covariance matrix $\boldsymbol{\hat{R}}_{yy}^{(q)}$ can be calculated as follows
% 	\begin{equation}\label{eq:eq03}
% 		\boldsymbol{\hat{R}}_{yy}^{(q)} = \frac{1}{N}\boldsymbol{Y}^{(q)}\boldsymbol{Y}^{(q)^{\rm T}}.
% 	\end{equation}

% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Proposed Framework
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Proposed Framework}

% 	For \textbf{probing} detection, compute the \textbf{sample covariance} $\boldsymbol{\hat{R}}_{zz}^{(q)}$ whose variables have \textbf{zero mean and unitary standard deviation} as follows
% 	\begin{equation}\label{eq:eq04}
% 		\boldsymbol{z}_{m}^{(q)} = \frac{\boldsymbol{x}_{m}^{(q)} - \bar{\boldsymbol{x}}_{m}^{(q)}}{\boldsymbol{\sigma}_{m}^{(q)}}.
% 	\end{equation}

% 	The sample covariance matrix $\boldsymbol{\hat{R}}_{zz}^{(q)}$ can be calculated via 
% 	\begin{equation}\label{eq:eq05}
% 		\boldsymbol{\hat{R}}_{zz}^{(q)} = \frac{1}{N}\boldsymbol{Z}^{(q)}\boldsymbol{Z}^{(q)^{\rm T}}.
% 	\end{equation}

% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Proposed Framework
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Proposed Framework}

% 	we refer to $\boldsymbol{\hat{R}}_{yy}$ and $\boldsymbol{\hat{R}}_{zz}$ as a matrix $\boldsymbol{C}$

% 	Compute eigenvalue decomposition (EVD) to obtain the vector of eigenvalues $\boldsymbol{e}^{(q)}$ associated with each matrix (time frame $q$), according to (\ref{eq:eq060}).
% 	\begin{equation}\label{eq:eq06}
% 	\boldsymbol{C}^{(q)} = \boldsymbol{V}^{(q)}\boldsymbol{\Lambda}^{(q)}\boldsymbol{V}^{(q)^{\rm T}},
% 	\end{equation}
% 	\begin{equation}\label{eq:eq060}
% 	\boldsymbol{e}^{(q)} = \rm diag(\boldsymbol{\Lambda}^{(q)}),
% 	\end{equation}

% 	The eigenvalues should be sorted in descending order, i.e., $\lambda_{1}^{(q)} > \lambda_{2}^{(q)} > \lambda_{3}^{(q)} > ... > \lambda_{m}^{(q)}$.

% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: Proposed Framework
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{Proposed Framework}

% 	\begin{equation}\label{eq:eq07}
% 		\boldsymbol{E} =
% 		\begin{bmatrix}
% 			\color{red}\lambda_1^{(1)} & \color{red}\lambda_1^{(2)} & \color{red}\lambda_1^{(3)} & \cdots & \color{red}\lambda_1^{(Q)} \\
% 			\lambda_2^{(1)} & \lambda_2^{(2)} & \lambda_2^{(3)} & \cdots & \lambda_2^{(Q)} \\
% 			\lambda_3^{(1)} & \lambda_3^{(2)} & \lambda_3^{(3)} & \cdots & \lambda_3^{(Q)} \\
% 			\vdots & \vdots & \ddots & \vdots  \\
% 			\lambda_m^{(1)} & \lambda_m^{(2)} & \lambda_m^{(3)} & \cdots & \lambda_m^{(Q)} \\
% 		\end{bmatrix}.
% 	\end{equation}

% 	\begin{equation}\label{eq:eq08}
% 		\boldsymbol{e}_{\rm max} = \boldsymbol{E}\{:,1\} = [ \lambda_1^{(1)}, \lambda_1^{(2)} ... \lambda_1^{(Q)}]
% 	\end{equation}

% \end{frame}
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% %	FRAME: MOS Scheme
% %-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
% \begin{frame}{MOS Scheme}

% 	\begin{itemize}
% 		\item Traditionally the MOS schemes are applied for the eigenvalues of the vector $\boldsymbol{e}^{(q)}$;
% 		\item $\boldsymbol{e}_{\rm max}$ is sorted in descending order, producing $\sim\boldsymbol{e}_{\rm max}$, that is used as input parameter for MOS schemes, according to $\hat{d} = \rm{MOS}(\sim\boldsymbol{e}_{\rm max})$.
% 		\item $\hat{d}$ is the estimated number of time frames under attack.
% 	\end{itemize}

% \end{frame}
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
%	FRAME: Eigenvalue Analysis
%-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
\begin{frame}{Eigenvalue Analysis}

	\textbf{MOS} reveal the \textbf{number of attacks} and through \textbf{eigenvalue analysis} we identify the \textbf{time frames} $q$ under attack

@@

	\textbf{Eigen Similarity} Analysis attempts to identify \textbf{time and ports}.

	The \textbf{reference eigenvectors} $\boldsymbol{v}^{(q)}$ is calculated from the \textbf{traffic without attack}.

@@

	The resultant $\boldsymbol{X}_{(n)}$ is necessary to obtain $\boldsymbol{v}_{(n)}$

@@

	Our \textbf{approach} presents \textbf{average results} if compared to two well known and highly adopted \textbf{classifier algorithms for fraud detection} from mobile money transactions.
